---
title: "Graphs and Plots"
author: "VAhir"
date: "May 31, 2016"
output: 
  html_document:
    keep_md: TRUE
---

**Step 1**  
First step in this RMD file is to correct the data type of couple of  columns in input file.  
Here class output for Sale Price and Sale Date are printed before and after the handling.

```{r setup1, echo=F}
library(knitr)
setwd("../Analysis")
opts_chunk$set(echo = FALSE, cache=FALSE)
read_chunk('CorrectingDataTypes.R')
```

```{r CorrectingDataTypes}

```
  
**Step 2**  
Next part will create a final file that will be ready for analysis. 
You should be able to see "FinalQueensData.csv" in Data folder after this step.  

```{r setup2, echo=F}
library(knitr)
setwd("../Analysis")
opts_chunk$set(echo = FALSE, cache=FALSE)
read_chunk('RemovingOutliers.R')
```

```{r RemovingOutliers}

```

**Step 3**  
Now that the final file is present for creating charts/graphs, we will generate first plot.

```{r}

# Print current working directory
getwd()

# Setting current working directory to "Data" so we can access data file after modifications
setwd("../Data")

# Loading csv file to a data.frame.
raw_df <- read.csv("FinalQueensData.csv", header=T, quote="\"", fill=TRUE, stringsAsFactors = FALSE)
raw_df$SALE.PRICE <- as.integer(raw_df$SALE.PRICE)
raw_df$SALE.DATE <- as.Date(raw_df$SALE.DATE)


# Plotting a Price vs Sq Ft chart
plot(raw_df$SALE.PRICE, raw_df$GROSS.SQUARE.FEET, main= "Queens Price vs SQ FT", xlab ="Price", ylab="SQ FT")

```


**Step 4**  
Here we are creating a simple horizontal bar chart for dollar amount of properties sold.  
  
```{r}


# Print current working directory
getwd()

# Setting current working directory to "Data" so we can access data file after modifications
setwd("../Data")

# Loading csv file to a data.frame.
raw_df <- read.csv("FinalQueensData.csv", header=T, quote="\"", fill=TRUE, stringsAsFactors = FALSE)

# Converting data types for sale price and sale date.
raw_df$SALE.PRICE <- as.integer(raw_df$SALE.PRICE)
raw_df$SALE.DATE <- as.Date(raw_df$SALE.DATE)

sale.price <- raw_df$SALE.PRICE/100
sq.ft <- raw_df$gross.square.feet/10

sale.price <-as.integer(sale.price)
sq.ft <- as.integer(sq.ft)

barplot(sale.price, main="Queens Sale Price", xlab="Dollar Amount in Thousands", horiz=TRUE, names.arg=c("Properties Sold"))

```
